### 2004-06-24 Documentation/part1.tex
*** empty log message ***

\section{The treatment of external input}

@@

@@

\bi
\item
 Baseline, Target mass, Source power, running time
\item
 Matter density profile
\item
 Threshold function, efficiencies etc.
\ei

>>>>

\section{The treatment of external input}
\label{sec:externalinput}

@@

\example{The impact of systematics, correlations, and degeneracies}{
\label{ex:corrproj}
\index{Bar charts}
\index{Systematics on/off}

Here it is shown how one can successively include systematics, correlations,
and degeneracies at the example of the $\stheta$ sensitivity limit.
An important part of this example is how two switch the systematics off,
\ie, how to obtain the sensitivity limit from statistics only. Since
this example is very advanced, we only show the respective part of the code:
\begin{quote}
{\tt 
Here comes the code excerpt.
}
\end{quote}
The complete code can be found as ``example4.c'' with the software.

The returned lists of data then represent $\Delta \chi^2$ 
as function of the fit value of $\stheta$. The intersections of these
curves with the line $\Delta \chi^2 = 9$ give the $\stheta$ sensitivity
limits, where we do not include the $\mathrm{sgn}(\ldm)$- and $(\deltacp,\theta_{13})$-degeneracies in the sensitivity limit with
correlations only (green bar):
\begin{center}
\colorbox{white}{\includegraphics[width=7cm]{barsex}}

\end{center}
}

@@

\bi
\item
 Baseline, Target mass, Source power, running time
\item
 Matter density profile
\item
 Systematics
\item
 Threshold function, efficiencies etc.
\ei
